---
title: "maize CAGE-seq manuscript figures and tables"
output:
  pdf_document:
    citation_package: natbib
    keep_tex: false
    fig_caption: true
    latex_engine: lualatex
# author:
# - name: Peng Zhou
#  affiliation: University of Minnesota
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 11pt
geometry: "left=0.5in,right=0.5in,top=0.8in,bottom=0.5in"
# spacing: double
# biblio-style: apsr
header-includes:
- \PassOptionsToPackage{table}{xcolor}
- \usepackage{fontspec}
- \setmainfont[Scale=MatchUppercase]{TeX Gyre Heros}
- \usepackage{caption}
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage[table]{xcolor}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \captionsetup[figure]{labelformat=empty}
- \captionsetup[table]{labelformat=empty}
- \AtBeginDocument{\let\maketitle\relax}
- \usepackage{lscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
---
\pagenumbering{gobble}

```{r, message=FALSE, echo=FALSE}
dirf = '/home/springer/zhoux379/projects/cage/data/95_figures/plots'
options(tinytex.verbose = TRUE)
```

\hfill

![](plots/f1.pdf){width=60%}

Figure 1. 


\pagebreak


Figure S1. 

\pagebreak
![](plots/sf02.pdf){width=50%}

Figure S2. TSS shape comparison between maize and three other species.


\pagebreak
![](plots/sf03.pdf){width=50%}

Figure S3. CAGE tag mapping rates for B73 and A632 samples.


\pagebreak
![](plots/sf03b.pdf){width=60%}

Figure S3b. t-SNE clustering of all samples.


\pagebreak
![](plots/f2.pdf){width=100%}

Figure 2. Shifting scores.


\pagebreak
Table 1. TSSs identified in the study.
```{r, message=FALSE, echo=FALSE}
readRDS(file.path(dirf, 'st1.rds'))
```
